Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-03 MS/ms.Rmd
small fixes.

As is clear from Table \@ref(tab:tablea) none of the effect measures control for 'nusance heterogenity'. For example, the magnitude of response between two treatment groups for lnRR or SMD might depend on just how different the tempeartures, dosages, pH or water potential applied in each treatment. Even modelling just the mean often needs to account for 'nusance heterogenity'. For example, standard metabolic rate (SMR) is tempearture dependent. As such, one needs to standardise the temperature measurement to compare across studies [@White2006; @Uyeda2017; if, of course, temperature is not of interest in of itself]. While we could of course model this explictly, this may not always be desireable. It can often be useful to standardise the effect to both ease its interpretation and simplify modelling. In Box 1 we provide readers with guidance on how comparative physiologists can apply corrections to the effect measure itself. We highlight two examples in the box focusing mainly on generality. Below, we show using a common well understood effect measure of interest to comparative physiologys, $Q_{10}$ how we can formalise a common effect size measure $lnRR$ to capture this 'nusance variation'.

>>>>

As is clear from Table \@ref(tab:tablea) none of the effect measures control for 'nusance heterogenity'. For example, the magnitude of response between two treatment groups for lnRR or SMD might depend on just how different the tempeartures, dosages, pH or water potential applied in each treatment. Even modelling just the mean often needs to account for 'nusance heterogenity'. For example, standard metabolic rate (SMR) is tempearture dependent. As such, one needs to standardise the temperature measurement to compare across studies [@White2006; @Uyeda2017, if, of course, temperature is not of interest in of itself]. While we could of course model this explictly, this may not always be desireable. It can often be useful to standardise the effect to both ease its interpretation and simplify modelling. In Box 1 we provide readers with guidance on how comparative physiologists can apply corrections to the effect measure itself. We highlight two examples in the box focusing mainly on generality. Below, we show using a common well understood effect measure of interest to comparative physiologys, $Q_{10}$ how we can formalise a common effect size measure $lnRR$ to capture this 'nusance variation'.
